---
title: "13_mpa_dewinter_adults_simdig_2"
output: html_document
---

## Corresponds to paper from MMF -> literature -> 13_Model

## **Population pharmacokinetics of mycophenolic acid, a comparison between enteric-coated mycophenlate sodium and mycophenolate mofetil in renal transplant recipients**
## de Winter, Brenda
## 2008, Clin Pharmacokinet


### Trial Design
* Retrospective, 184 renal transplant patients
* The data were obtained from 7 clinical trials and 2 unpublished studies.
* Dose: MPA equivalents of 1000 (250-2200) mg. The paper reported MPA equivalents which were converted from MMF by multiplying the dose by 0.739.
* Co-medication: cyclosporine 178 (53-522) mg
* Sampling strategy: Tedesco-Silva: 0-12 hr, 13 samples; Van Gelder: 0-2 hr, 5 samples; Pescovitz: 0-12 hr, 10 samples


### Patient demographics: median (range)
* Gender: M=89, F=55
* WT (kg): 73 (44-108)
* Age (yr): 51 (19-74)
* Scr (mcgmol/L): 130 (79-280)
* Clcr (L/hr): 3.5 (1.5-7.4)
* Alb (g/L): 39 (32-53)


### Model Structure
* A 2-compartment model with first-order elimination with delayed absorption characterized by a lag-time and a first-order absorption process


```{r}

library(tidyverse)
library(PKPDmisc)
library(mrgsolve)
library(dmutate)

library(ggplot2)
library(purrr)

library(overseer)
library(satchel)

```


```{r}

#####
# Importing demographics datasets using satchel
#####

satchel <- Satchel$new("demographics_sim", "../data/derived/satchel")

satchel$available()

demog1 <- satchel$use("mpa_01_shum_adults_demog")
demog2 <- satchel$use("mpa_02_guellec_adults_demog")
demog3 <- satchel$use("mpa_03_staatz_adults_demog")
demog5 <- satchel$use("mpa_05_vanhest_adults_demog")
demog13 <- satchel$use("mpa_13_dewinter_adults_demog")
demog4 <- satchel$use("mpa_04_payen_peds_demog")
demog7 <- satchel$use("mpa_07_premaud_peds_demog")
demog21 <- satchel$use("mpa_21_zhao_peds_demog")
demog22 <- satchel$use("mpa_22_dong_peds_demog")
demog23 <- satchel$use("mpa_23_zhao_peds_demog")

```


```{r}

#####
# Importing mpa models using overseer
#####

## provides list MODELS containing models

models <- source("../modeling/models.R")$value

models$available()

model <- models$use("13_mpa_dewinter_adults")

```


```{r}

#####
# Simulation of adults individual CL, Vc, CP, and IPRED
#####

## For adults demog datasets: 01, 02, 03, 05, 13


LLOQ <- 0

sim_01 <- model %>% data_set(demog1) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)

sim_02 <- model %>% data_set(demog2) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)

sim_03 <- model %>% data_set(demog3) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)

sim_05 <- model %>% data_set(demog5) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)

sim_13 <- model %>% data_set(demog13) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)


ggplot(sim_01, aes(x=time, y=CP)) + geom_point() 


```


```{r}

#####
# Simulation of pediatrics individual CL, Vc, CP, and IPRED
#####

## For pediatrics demog datasets: 04, 07, 21, 22, 23


sim_04 <- model %>% data_set(demog4) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)

sim_07 <- model %>% data_set(demog7) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)

sim_21 <- model %>% data_set(demog21) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)

sim_22 <- model %>% data_set(demog22) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)

sim_23 <- model %>% data_set(demog23) %>%
  carry.out(time, dose, amt, cmt, evid, ii, addl) %>% 
  mrgsim(start=0.1, end=12, delta=0.05) %>% as.data.frame() %>% filter(CP>=LLOQ)


ggplot(sim_04, aes(x=time, y=CP)) + geom_point() 



```


```{r}

#####
# Take mean concentrations at each time point and filter for sampling time points 
#####

sim_01a <- sim_01 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))
sim_02a <- sim_02 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))
sim_03a <- sim_03 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))
sim_05a <- sim_05 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))
sim_13a <- sim_13 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))

sim_04a <- sim_04 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))
sim_07a <- sim_07 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))
sim_21a <- sim_21 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))
sim_22a <- sim_22 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))
sim_23a <- sim_23 %>% group_by(time) %>% mutate(mean_cp_sim=mean(CP)) %>% ungroup %>% mutate(time=as_numeric(time))

```


```{r}

#####
# Filter for sampling time points
#####

## Model 01: 0.25, 0.5, 0.75, 1, 1.25, 1.5, 2, 3, 4, 6, 8, 10, 12 hrs
## Model 02: 0.33, 0.66, 1, 1.5, 2, 3, 4, 6, 9 hrs
## Model 03: 0, 1, 2, 3, 4 hrs
## Model 05: 0.33, 0.66, 1.25, 2, 6, 8, 12 hrs
## Model 13: 0, 0.25, 0.33, 0.5, 0.66, 0.75, 1, 1.25, 1.5, 2, 2.5, 3, 4, 5, 6, 8, 10, 12 hrs


## Model 04: 0, 1, 2, 4, 6, 8, 10, 12 hrs
## Model 07: 0, 0.33, 0.66, 1, 1.5, 2, 3, 4, 6, 9, 12 hrs
## Model 21: 0, 0.5, 1, 2, 3, 4, 6, 8, 12 hrs
## Model 22: 0, 0.33, 0.66, 1, 1.5, 2, 3, 4, 6, 9 hrs
## Model 23: 0, 0.5, 1, 2, 4, 8, 12 hrs

## Modifying time points to match the digitized time points

sample_time1 <- c(0.25, 0.75, 1.5, 2, 3, 4, 6, 12) 
sample_time2 <- c(0, 0.3, 0.6, 1, 1.5, 3, 4, 6, 9)
sample_time3 <- c(0, 1, 2, 3, 4)
sample_time5 <- c(0, 0.3, 0.6, 1, 1.5, 3, 4, 6, 9)
sample_time13 <- c(0, 0.25, 0.3, 0.5, 0.6, 0.75, 1, 1.25, 1.5, 2, 2.5, 3, 4, 5, 6, 8, 10, 12)
  
sample_time4 <- c(0, 0.5, 1, 2, 6, 12)
sample_time7 <- c(0.3, 0.6, 1, 1.5, 2, 3, 4, 6, 9, 12)
sample_time21 <- c(0, 0.5, 3, 4, 6, 8, 10, 12)
sample_time22 <- c(0.6, 1, 1.5, 2, 3, 4, 6, 9)
sample_time23 <- c(0, 0.5, 1, 2, 4, 8, 12)

sim_01b <- sim_01a %>% filter(time%in%sample_time1) %>% filter(ID==1) %>% mutate(model=1) %>% select(time, mean_cp_sim, model)

sim_02b <- sim_02a %>% filter(time%in%sample_time2) %>% filter(ID==1) %>% mutate(model=2) %>% select(time, mean_cp_sim, model)

sim_03b <- sim_03a %>% filter(time%in%sample_time3) %>% filter(ID==1) %>% mutate(model=3) %>% select(time, mean_cp_sim, model) 

sim_05b <- sim_05a %>% filter(time%in%sample_time5) %>% filter(ID==1) %>% mutate(model=5) %>% select(time, mean_cp_sim, model) 

sim_13b <- sim_13a %>% filter(time%in%sample_time13) %>% filter(ID==1) %>% mutate(model=13) %>% select(time, mean_cp_sim, model)


sim_04b <- sim_04a %>% filter(time%in%sample_time4) %>% filter(ID==1) %>% mutate(model=4) %>% select(time, mean_cp_sim, model)

sim_07b <- sim_07a %>% filter(time%in%sample_time7) %>% filter(ID==1) %>% mutate(model=7) %>% select(time, mean_cp_sim, model)

sim_21b <- sim_21a %>% filter(time%in%sample_time21) %>% filter(ID==1) %>% mutate(model=21) %>% select(time, mean_cp_sim, model)

sim_22b <- sim_22a %>% filter(time%in%sample_time22) %>% filter(ID==1) %>% mutate(model=22) %>% select(time, mean_cp_sim, model) 

sim_23b <- sim_23a %>% filter(time%in%sample_time23) %>% filter(ID==1) %>% mutate(model=23) %>% select(time, mean_cp_sim, model) 


```


```{r}

#####
# Renaming time to TAD
#####

sim_01b <- rename(sim_01b, TAD = time) 
sim_02b <- rename(sim_02b, TAD = time) 
sim_03b <- rename(sim_03b, TAD = time)
sim_05b <- rename(sim_05b, TAD = time)
sim_13b <- rename(sim_13b, TAD = time)

sim_04b <- rename(sim_04b, TAD = time)
sim_07b <- rename(sim_07b, TAD = time)
sim_21b <- rename(sim_21b, TAD = time)
sim_22b <- rename(sim_22b, TAD = time)
sim_23b <- rename(sim_23b, TAD = time)
       
```


```{r}

#####
# Read in digitized observed pk profiles
#####

dig_01 <- read.csv("../data/original/01_Shum_1e_v3.csv")
dig_02 <- read.csv("../data/original/02_Guellec_1a.csv")
dig_03 <- read.csv("../data/original/03_Staatz_1.csv")
dig_05 <- read.csv("../data/original/05_vanHest_1a.csv")
dig_13 <- read.csv("../data/original/13_deWinter_1b.csv")
  
dig_04 <- read.csv("../data/original/04_Payen_6b.csv")
dig_07 <- read.csv("../data/original/07_Premaud_3a.csv")
dig_21 <- read.csv("../data/original/21_Zhao_4.csv")
dig_22 <- read.csv("../data/original/22_Dong_3.csv")
dig_23 <- read.csv("../data/original/23_Zhao_2.csv")

```

```{r}

#####
# Bin dig to sample times
#####

dig_01a <- dig_01 %>% mutate(TAD=ifelse(between(time, 0, 0.25), 0, time),
                                             TAD=ifelse(between(time, 0.25, 0.5), 0.25, TAD),
                                             TAD=ifelse(between(time, 0.5, 0.75), 0.5, TAD),
                                             TAD=ifelse(between(time, 0.75, 1), 0.75, TAD),
                                             TAD=ifelse(between(time, 1, 1.25), 1, TAD),
                                             TAD=ifelse(between(time, 1.25, 1.5), 1.25, TAD),
                                             TAD=ifelse(between(time, 1.5, 2), 1.5, TAD),
                                             TAD=ifelse(between(time, 2, 3), 2, TAD),
                                             TAD=ifelse(between(time, 3, 4), 3, TAD),
                                             TAD=ifelse(between(time, 4, 6), 4, TAD),
                                             TAD=ifelse(between(time, 6, 8), 6, TAD),
                                             TAD=ifelse(between(time, 8, 10), 8, TAD),
                                             TAD=ifelse(between(time, 10, 12), 10, TAD),
                                             TAD=ifelse(between(time, 12, 13), 12, TAD))

dig_02a <- dig_02 %>% mutate(TAD=ifelse(between(time, 0, 0.3), 0, time),
                                             TAD=ifelse(between(time, 0.3, 0.6), 0.3, TAD),
                                             TAD=ifelse(between(time, 0.6, 1), 0.6, TAD),
                                             TAD=ifelse(between(time, 1, 1.5), 1, TAD),
                                             TAD=ifelse(between(time, 1.5, 2), 1.5, TAD),
                                             TAD=ifelse(between(time, 2, 3), 2, TAD),
                                             TAD=ifelse(between(time, 3, 4), 3, TAD),
                                             TAD=ifelse(between(time, 4, 6), 4, TAD),
                                             TAD=ifelse(between(time, 6, 7), 6, TAD),
                                             TAD=ifelse(between(time, 7, 10), 9, TAD),
                                             TAD=ifelse(between(time, 10, 12), 12, TAD))

dig_03a <- dig_03 %>% mutate(TAD=ifelse(between(time, 0, 1), 0, time),
                                             TAD=ifelse(between(time, 1, 2), 1, TAD),
                                             TAD=ifelse(between(time, 2, 3), 2, TAD),
                                             TAD=ifelse(between(time, 3, 3.5), 3, TAD),
                                             TAD=ifelse(between(time, 3.5, 4), 4, TAD))
                                             

dig_05a <- dig_05 %>% mutate(TAD=ifelse(between(time, 0, 0.33), 0, time),
                                             TAD=ifelse(between(time, 0.33, 0.66), 0.3, TAD),
                                             TAD=ifelse(between(time, 0.66, 1.25), 0.6, TAD),
                                             TAD=ifelse(between(time, 1.25, 2), 1.25, TAD),
                                             TAD=ifelse(between(time, 2, 6), 2, TAD),
                                             TAD=ifelse(between(time, 6, 8), 6, TAD),
                                             TAD=ifelse(between(time, 8, 10), 8, TAD),
                                             TAD=ifelse(between(time, 10, 12), 12, TAD))

dig_13a <- dig_13 %>% mutate(TAD=ifelse(between(time, 0, 0.25), 0, time),
                                             TAD=ifelse(between(time, 0.25, 0.33), 0.25, TAD),
                                             TAD=ifelse(between(time, 0.33, 0.5), 0.3, TAD),
                                             TAD=ifelse(between(time, 0.5, 0.66), 0.5, TAD),
                                             TAD=ifelse(between(time, 0.66, 0.75), 0.6, TAD),
                                             TAD=ifelse(between(time, 0.75, 1), 0.75, TAD),
                                             TAD=ifelse(between(time, 1, 1.25), 1, TAD),
                                             TAD=ifelse(between(time, 1.25, 1.5), 1.25, TAD),
                                             TAD=ifelse(between(time, 1.5, 2), 1.5, TAD),
                                             TAD=ifelse(between(time, 2, 2.5), 2, TAD),
                                             TAD=ifelse(between(time, 2.5, 3), 2.5, TAD),
                                             TAD=ifelse(between(time, 3, 4), 3, TAD),
                                             TAD=ifelse(between(time, 4, 5), 4, TAD),
                                             TAD=ifelse(between(time, 5, 6), 5, TAD),
                                             TAD=ifelse(between(time, 6, 8), 6, TAD),
                                             TAD=ifelse(between(time, 8, 10), 8, TAD),
                                             TAD=ifelse(between(time, 10, 11), 10, TAD),
                                             TAD=ifelse(between(time, 11, 12), 12, TAD))


dig_04a <- dig_04 %>% mutate(TAD=ifelse(between(time, 0, 1), 0, time),
                                             TAD=ifelse(between(time, 0.5, 1), 0.5, TAD),
                                             TAD=ifelse(between(time, 1, 2), 1, TAD),
                                             TAD=ifelse(between(time, 2, 4), 2, TAD),
                                             TAD=ifelse(between(time, 4, 6), 4, TAD),
                                             TAD=ifelse(between(time, 6, 8), 6, TAD),
                                             TAD=ifelse(between(time, 8, 10), 8, TAD),
                                             TAD=ifelse(between(time, 10, 11), 10, TAD),
                                             TAD=ifelse(between(time, 11, 12.5), 12, TAD)) %>% filter(TAD<12.5)

dig_07a <- dig_07 %>% mutate(TAD=ifelse(between(time, 0, 0.33), 0, time),
                                             TAD=ifelse(between(time, 0.33, 0.66), 0.3, TAD),
                                             TAD=ifelse(between(time, 0.66, 1), 0.6, TAD),
                                             TAD=ifelse(between(time, 1, 1.5), 1, TAD),
                                             TAD=ifelse(between(time, 1.5, 2), 1.5, TAD),
                                             TAD=ifelse(between(time, 2, 3), 2, TAD),
                                             TAD=ifelse(between(time, 3, 4), 3, TAD),
                                             TAD=ifelse(between(time, 4, 6), 4, TAD),
                                             TAD=ifelse(between(time, 6, 9), 6, TAD),
                                             TAD=ifelse(between(time, 9, 11), 9, TAD),
                                             TAD=ifelse(between(time, 11, 12), 12, TAD))

dig_21a <- dig_21 %>% mutate(TAD=ifelse(between(time, 0, 0.4), 0, time),
                                             TAD=ifelse(between(time, 0.4, 1), 0.5, TAD),
                                             TAD=ifelse(between(time, 1, 2), 2, TAD),
                                             TAD=ifelse(between(time, 2, 3), 3, TAD),
                                             TAD=ifelse(between(time, 3, 4), 4, TAD),
                                             TAD=ifelse(between(time, 4, 7), 6, TAD),
                                             TAD=ifelse(between(time, 7, 8), 8, TAD),
                                             TAD=ifelse(between(time, 8, 10), 10, TAD),
                                             TAD=ifelse(between(time, 10, 12), 12, TAD)) %>%
                                             filter(treatment=="cyclosporine")

dig_22a <- dig_22 %>% mutate(TAD=ifelse(between(time, 0, 0.33), 0, time),
                                             TAD=ifelse(between(time, 0.33, 0.66), 0.3, TAD),
                                             TAD=ifelse(between(time, 0.66, 1), 0.6, TAD),
                                             TAD=ifelse(between(time, 1, 1.5), 1, TAD),
                                             TAD=ifelse(between(time, 1.5, 2), 1.5, TAD),
                                             TAD=ifelse(between(time, 2, 3), 2, TAD),
                                             TAD=ifelse(between(time, 3, 4), 3, TAD),
                                             TAD=ifelse(between(time, 4, 6), 4, TAD),
                                             TAD=ifelse(between(time, 6, 8), 6, TAD),
                                             TAD=ifelse(between(time, 8, 10), 9, TAD))

dig_23a <- dig_23 %>% mutate(TAD=ifelse(between(time, 0, 0.5), 0, time),
                                             TAD=ifelse(between(time, 0.5, 1), 0.5, TAD),
                                             TAD=ifelse(between(time, 1, 2), 1, TAD),
                                             TAD=ifelse(between(time, 2, 4), 2, TAD),
                                             TAD=ifelse(between(time, 4, 8), 4, TAD),
                                             TAD=ifelse(between(time, 8, 10), 8, TAD),
                                             TAD=ifelse(between(time, 10, 12), 12, TAD))
                                             
 
```



```{r}

#####
# Take mean of cp of each bin in TAD and take unique values
#####

dig_01b <- dig_01a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp)) %>% distinct(mean_cp_dig) %>%
                                         mutate(model=01)

dig_02b <- dig_02a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp)) %>% distinct(mean_cp_dig) %>%
                                         mutate(model=02)

dig_03b <- dig_03a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp2)) %>% distinct(mean_cp_dig) %>% 
                                         mutate(model=03)

dig_05b <- dig_05a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp)) %>% distinct(mean_cp_dig) %>% 
                                         mutate(model=05)

dig_13b <- dig_13a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp)) %>% distinct(mean_cp_dig) %>% 
                                         mutate(model=13)

dig_04b <- dig_04a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp)) %>% distinct(mean_cp_dig) %>% 
                                         mutate(model=04)

dig_07b <- dig_07a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp)) %>% distinct(mean_cp_dig) %>% 
                                         mutate(model=07)

dig_21b <- dig_21a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp)) %>% distinct(mean_cp_dig) %>% 
                                         mutate(model=21)

dig_22b <- dig_22a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp)) %>% distinct(mean_cp_dig) %>% 
                                         mutate(model=22)

dig_23b <- dig_23a %>% group_by(TAD) %>% mutate(mean_cp_dig=mean(cp)) %>% distinct(mean_cp_dig) %>% 
                                         mutate(model=23)


```


```{r}

#####
# Combining all the dig data
#####

dig_all <- rbind(dig_01b, dig_02b, dig_03b, dig_05b, dig_13b, dig_04b, dig_07b, dig_21b, dig_22b, dig_23b) %>% mutate(data="dig")

sim_all <- rbind(sim_01b, sim_02b, sim_03b, sim_05b, sim_13b, sim_04b, sim_07b, sim_21b, sim_22b, sim_23b) %>% mutate(data="sim")


```


```{r}

#####
# Read in combined dataset
#####

sim_dig <- read.csv("../data/derived/01_Sim_Dig.csv")


```


```{r}

#####
# Subtract the dig concentration from the sim concentration at each time point
#####


sim_dig_diff <- sim_dig %>% mutate(sim_dig_diff=mean_cp_sim - mean_cp_dig) %>% mutate(squares=sim_dig_diff*sim_dig_diff)


sum(sim_dig_diff$squares)


```


```{r}

#####
# Calculating the AUC for dig and sim curves. 1a=sim, 1b=dig original
#####

auc1a <- auc_partial(sim_01b$TAD, sim_01b$mean_cp_sim, range=c(0, 12.23)) 
  auc1b <- auc_partial(dig_01$time, dig_01$cp, range=c(0, 12.23))
  
  
auc2a <- auc_partial(sim_02b$TAD, sim_02b$mean_cp_sim, range=c(0, 8.99)) 
  auc2b <- auc_partial(dig_02$time, dig_02$cp, range=c(0, 8.99))
  
  
auc3a <- auc_partial(sim_03b$TAD, sim_03b$mean_cp_sim, range=c(0, 4)) 
  auc3b <- auc_partial(dig_03$time, dig_03$cp2, range=c(0, 3.99))
  
  
auc5a <- auc_partial(sim_05b$TAD, sim_05b$mean_cp_sim, range=c(0, 11.92)) 
  auc5b <- auc_partial(dig_05$time, dig_05$cp, range=c(0, 11.92))
  
  
auc13a <- auc_partial(sim_13b$TAD, sim_13b$mean_cp_sim, range=c(0, 11.94)) 
  auc13b <- auc_partial(dig_13$time, dig_13$cp, range=c(0, 11.94))
  
  
auc4a <- auc_partial(sim_04b$TAD, sim_04b$mean_cp_sim, range=c(0, 12.64)) 
  auc4b <- auc_partial(dig_04$time, dig_04$cp, range=c(0, 12.64))
  
  
auc7a <- auc_partial(sim_07b$TAD, sim_07b$mean_cp_sim, range=c(0, 11.86)) 
  auc7b <- auc_partial(dig_07$time, dig_07$cp, range=c(0, 11.86))

  
auc21a <- auc_partial(sim_21b$TAD, sim_21b$mean_cp_sim, range=c(0, 11.95)) 
  auc21b <- auc_partial(dig_21a$time, dig_21a$cp, range=c(0, 11.95))
  
  
auc22a <- auc_partial(sim_22b$TAD, sim_22b$mean_cp_sim, range=c(0, 9.01)) 
  auc22b <- auc_partial(dig_22$time, dig_22$cp, range=c(0, 9.01))
  
  
auc23a <- auc_partial(sim_23b$TAD, sim_23b$mean_cp_sim, range=c(0, 11.95)) 
  auc23b <- auc_partial(dig_23$time, dig_23$cp, range=c(0, 11.95))
 

#####
# Creating a table for calcuated AUCs
#####

model <- c(1,2,3,5,13,4,7,21,22,23)
  
auc_sim <- c(auc1a, auc2a, auc3a, auc5a, auc13a, auc4a, auc7a, auc21a, auc22a, auc23a)
  
auc_dig <- c(auc1b, auc2b, auc3b, auc5b, auc13b, auc4b, auc7b, auc21b, auc22b, auc23b)

auc_all <- data.frame(Model=model, AUC_Sim=auc_sim, AUC_Dig=auc_dig)

auc_all

auc_all <- auc_all %>% mutate(Diff_AUC=AUC_Sim - AUC_Dig) %>% mutate(SSR=Diff_AUC*Diff_AUC)

auc_all

sum(auc_all$SSR)
  
```


```{r}

#####
# Plots of simulation vs observed pk profiles. Red=simulation, black=observed
#####

plot1 <- ggplot(sim_01a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_01, aes(x=time, y=cp)) + geom_line(data=dig_01, aes(x=time, y=cp)) + labs(title="Shum")

plot1

plot2 <- ggplot(sim_02a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_02, aes(x=time, y=cp)) + geom_line(data=dig_02, aes(x=time, y=cp)) + labs(title="Guellec")

plot2

plot3 <- ggplot(sim_03a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_03, aes(x=time, y=cp2)) + geom_line(data=dig_03, aes(x=time, y=cp2)) + labs(title="Staatz")

plot3

plot5 <- ggplot(sim_05a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_05, aes(x=time, y=cp)) + geom_line(data=dig_05, aes(x=time, y=cp)) + labs(title="van Hest")

plot5

plot13 <- ggplot(sim_13a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_13, aes(x=time, y=cp)) + geom_line(data=dig_13, aes(x=time, y=cp)) + labs(title="de Winter")

plot13

plot4 <- ggplot(sim_04a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_04a, aes(x=time, y=cp)) + geom_line(data=dig_04a, aes(x=time, y=cp)) + labs(title="Payen")

plot4

plot7 <- ggplot(sim_07a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_07, aes(x=time, y=cp)) + geom_line(data=dig_07, aes(x=time, y=cp)) + labs(title="Premaud")

plot7

plot21 <- ggplot(sim_21a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_21, aes(x=time, y=cp)) + geom_line(data=dig_21, aes(x=time, y=cp)) + labs(title="Zhao")

plot21

plot22 <- ggplot(sim_22a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_22, aes(x=time, y=cp)) + geom_line(data=dig_22, aes(x=time, y=cp)) + labs(title="Dong")

plot22

plot23 <- ggplot(sim_23a, aes(x=time, y=mean_cp_sim)) + geom_point(color="red") + geom_line(color="red") + geom_point(data=dig_23, aes(x=time, y=cp)) + geom_line(data=dig_23, aes(x=time, y=cp)) + labs(title="Zhao")

plot23

```


```{r}

devtools::session_info()

```


